Quantifying the importance of an inference model in Bayesian phylogenetics

### 2020-07-29 pirouette_article.tex
Reviewed changes for review

\begin{figure}[H]
  \includegraphics[width=0.9\textwidth]{pirouette_example_30/errors.png}
  \caption{
    \new{
      The impact of the tree prior for 
      the example tree in Figure \ref{fig:dd_tree}. 
      The alignment for this true tree was generated using a JC substitution model 
      and strict clock model. 
      For inferring the tree from this alignment in the 'generative' scenario,
      the same substitution and clock models were used, 
      and a Yule tree prior (this is the assumed generative model,
      because the real generative model is of course unknown).
      For the twin tree, the same inference model is used.
      In the 'best' scenarios, for the 'true' tree, 
      the best-fitting candidate models on the 'true' tree
      (JC substitution model, RLN clock model and BD tree prior) 
      was used. 
      In the 'best' scenarios, for the 'twin' tree, 
      the best-fitting candidate models on the 'twin' tree
      (JC substitution model, RLN clock model and Yule tree prior) 
      was used. 
      The twin distributions show the baseline inference error.
    }
    Vertical dashed lines show the median error value per distribution.
  }
  \label{fig:example_30}
\end{figure}

>>>>

\begin{figure}[H]
  \includegraphics[width=0.9\textwidth]{pirouette_example_30/errors.png}
  \caption{
    \new{
      The impact of the tree prior for 
      the example tree in Figure \ref{fig:dd_tree}. 
      The alignment for this true tree was generated using a JC substitution model 
      and strict clock model. 
      For inferring the tree from this alignment in the 'generative' scenario,
      the same substitution and clock models were used, 
      and a Yule tree prior (this is the assumed generative model,
      because the real generative model is of course unknown).
      For the twin tree, the same inference model is used.
      In the 'best' scenario, for the true tree, 
      the best-fitting candidate models on the true tree
      (JC substitution model, RLN clock model and BD tree prior) 
      was used. 
      In the 'best' scenario, for the twin tree, 
      the best-fitting candidate models on the twin tree
      (JC substitution model, RLN clock model and Yule tree prior) 
      was used. 
      The twin distributions show the baseline inference error.
    }
    Vertical dashed lines show the median error value per distribution.
  }
  \label{fig:example_30}
\end{figure}

### 2020-07-29 pirouette_supplement.tex
Reviewed changes for review

The pipeline starts at the top-left panel of figure \ref{fig:pipeline} (which 
is identical to figure \ref{fig:dd_tree}),
which is the 'true tree'.
The 'true tree' is generated by the diversity-dependent (DD) 
tree model [\citep{DDD, etienne2012diversity}],
which is a BD model with a speciation rate that is dependent on the number of species,
with (an arbitrarily chosen) crown age of 10 time units 
and an expected number of 6 tips for an extinction rate of 0.1. 
The carrying-capacity is set to 6. 
The initial speciation rate $\lambda_0$ is chosen 
such that the expected number of species in a constant-rate BD model 
would be equal to the number of tips, which amounts to $\lambda_0 = 0.63$.
Note that in the main example, a tree was generated with 5 tips, due
to stochasticity in the tree generation algorithm.

@@

Based on the 'twin alignment' (center-right panel), the candidate model
with the highest marginal likelihood is determined, from the same 
set of 15 candidate models.The inference model that had the
highest evidence (as shown in Table \ref{tab:evidence_twin}) was 
the inference model with a JC nucleotide substitution model,
an RLN clock model and a Yule tree model (note: this indeed matches how
the twin tree and twin tree were simulated).
From the 'twin alignment' this best candidate inference model is run.
The resulting posterior trees are shown in the fourth panel
of the third row of posteriors in figure \ref{fig:pipeline}.

>>>>

The pipeline starts at the top-left panel of figure \ref{fig:pipeline} (which 
is identical to figure \ref{fig:dd_tree}),
which is the 'true tree'.
The 'true tree' is generated by the diversity-dependent (DD) 
tree model [\citep{DDD, etienne2012diversity}],
which is a BD model with a speciation rate that is dependent on the number of species,
with (an arbitrarily chosen) crown age of 10 time units 
and an expected number of 6 tips for an extinction rate of 0.1. 
The carrying-capacity is set to 6. 
The initial speciation rate $\lambda_0$ is chosen 
such that the expected number of species in a constant-rate BD model 
would be equal to the number of tips, which amounts to $\lambda_0 = 0.63$.
\new{
  Note that in the main example, a tree was generated with 5 tips, due
  to stochasticity in the tree generation algorithm.
}

@@

Based on the 'twin alignment' (center-right panel), the candidate model
with the highest marginal likelihood is determined, from the same 
set of 15 candidate models.The inference model that had the
highest evidence (as shown in Table \ref{tab:evidence_twin}) was 
the inference model with a JC nucleotide substitution model,
an RLN clock model and a Yule tree model 
\new{
  (note: this mismatches how
  the twin tree and twin tree were simulated, as the twin tree
  is generated using a BD process, where the alignment
  is simulated using a JC substitution model and strict clock model
  ).
}
From the 'twin alignment' this best candidate inference model is run.
The resulting posterior trees are shown in the fourth panel
of the third row of posteriors in figure \ref{fig:pipeline}.
